---
title: "Supplemental Material for Infanticide" 
output: word_document
---

```{r setup, include=FALSE, echo = FALSE}

library(coda)
library(brms)
load('Data/age_model.RData')
load('Data/prey_and_cub_models.RData')

```

## Model detail and diagnostic for moratlity ~ age at death 

Here we used a multinomial model of mortality source as a function of age at death
to understand the contribution of different mortality sources to overall mortality. 
This model was initialized with weak, uninformative priors, and three chains were run for 15000 iterations each (7500 warmup). 

#### Model summary

```{r age at death model - summary}

# Priors
prior_summary(fit)

summary(fit)
```
## Model diagnostics

Traceplots indicate convergence, and all R-hat values are equal to 1. Geweke's 
diagnostic indicates that the chains achieved stability. The MCMC chains showed minimal autocorrelation. 

```{r age at death model - traceplots}
## Model checking
## For use with coda package
coda.model <- brms::as.mcmc(fit)

## Check for adequate convergence
gelman.diag(coda.model) ## Equals 1
par(mfrow = c(3, 3))
plot(fit) ## Traceplots indicate convergence
geweke.diag(coda.model) ## All less extreme than 1.96
heidel.diag(coda.model)
autocorr.plot(coda.model) ## Autocorrelation looks fine
```

