---
title: "Supplemental Material for Infanticide" 
output: word_document
---

```{r setup, include=FALSE, echo = FALSE}

library(brms)
load('Data/age_model.RData')
load('Data/prey_and_cub_models.RData')

```

## Model detail and diagnostic for moratlity ~ age at death 

Here we used a multinomial model of mortality source as a function of age at death
to understand the contribution of different mortality sources to overall mortality. 
This model was initialized with weak, uninformative priors, and three chains were run for 15000 iterations each (7500 warmup). 

#### Model summary and diagnostic

```{r age at death model - summary}

# Priors
prior_summary(fit)

summary(fit)

par(mfrow = c(3, 3))
mcmc_plot(fit, type = 'trace') ## Traceplots indicate convergence

rhat(fit)
```
## Model detail and diagnostic for prey density ~ mortality + (1|clan) 

Here we built a mixed model of prey density in the month before death as a function of mortality source, including a random effect of clan.
This model was initialized with weak, uninformative priors, and four chains were run for 2000 iterations each (1000 warmup). 

#### Model summary and diagnostic

```{r prey model - summary}

# Priors
prior_summary(prey_mod)

summary(prey_mod)

par(mfrow = c(3, 3))
mcmc_plot(prey_mod, type = 'trace') ## Traceplots indicate convergence

rhat(prey_mod)
```

## Model detail and diagnostic for cub density ~ mortality + (1|clan) 

Here we built a mixed model of prey density in the month before death as a function of mortality source, including a random effect of clan.
This model was initialized with weak, uninformative priors, and four chains were run for 2000 iterations each (1000 warmup). 

#### Model summary and diagnostic

```{r cub density model - summary}

# Priors
prior_summary(cub_density_mod)

summary(cub_density_mod)

par(mfrow = c(3, 3))
mcmc_plot(cub_density_mod, type = 'trace') ## Traceplots indicate convergence

rhat(cub_density_mod)
```



